%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setstretch{1.1}

\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-1pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-3pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0.2em, topsep=0.2em]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0.2em, topsep=0.2em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Baraa Bilal El Baba} \\ \vspace{1pt}
    \small Full-Stack Developer (Frontend-Focused) \\ \vspace{1pt}
    \small Saida, Lebanon $|$ 76-032-809 $|$ 
    \href{mailto:baraababawork@gmail.com}{\underline{baraababawork@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/baraa-el-baba-336262264/}{\underline{linkedin.com/in/baraa-baba}} $|$
    \href{https://github.com/Baraa-Baba}{\underline{github.com/Baraa-Baba}} 
\end{center}
 

%-----------EDUCATION-----------
\section*{Education}
\textbf{Rafik Hariri University (RHU)} \hfill Saida, Lebanon \\
\textit{Bachelor of Science in Computer Science} \hfill \textit{August 2024 -- May 2027} \\
\vspace{-0.2em}
{\footnotesize
\resumeItemListStart
    \resumeItem{\textbf{CGPA:} 91/100, Ranked 1st in Computer Science}
    \resumeItem{\textbf{Scholarship:} 50\% merit scholarship for high school web competition}
\resumeItemListEnd
\vspace{-2pt}
}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Front-End Web Developer}{May 2023 -- Present}
  {OctaSolutions.co}{Saida, Lebanon}
  \resumeItemListStart 
    \resumeItem{Designed and developed a reusable, design-agnostic e-commerce library using Vue.js (cart, checkout, product state, authentication).}  
    \resumeItem{Built the frontend of \href{https://octadine.com/restaurant}{OctaDine}, a digital menu web app using Vue, Leaflet, and Git.}
    \resumeItem{Developed 30+ webpages for \href{https://parisaline.com/}{parisaline.com} and \href{https://renaissance-translations.com/}{renaissance-translations.com}.} 
    \resumeItem{Maintained legacy code for an internal company framework.}
    \resumeItem{Replicated an existing company app in Flutter for training purposes.}
    \resumeItem{Set up a CodePush standalone server using SSH and Docker.}
  \resumeItemListEnd

\resumeSubheading
  {Full-Stack Web Developer}{}
  {Freelance}{Online}
  \resumeItemListStart 
    \resumeItem{Built \href{https://chatandplay.onrender.com/}{Chat \& Play}, a real-time social web app with peer-to-peer communication and multiplayer games like chess.} 
    \resumeItem{Developed and deployed \href{https://modelonetrading.com}{modelonetrading.com} (React) and \href{https://duratex.co}{duratex.co} (Vue.js), including domain and email setup, and scraped products from the orignal website for \href{https://duratex.co}{duratex.co}.} 
    \resumeItem{Built and deployed \href{https://fancy-clancy.com}{fancy-clancy.com}, a Vue.js e-commerce website with Supabase backend, including an admin dashboard and WhatsApp-based ordering.}
    \resumeItem{Consulted with 10+ clients to debug production issues and implement features, improving stability and UX.}   
  \resumeItemListEnd

\resumeSubHeadingListEnd
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{E-commerce Core Logic Library} $|$ \emph{Vue.js, JavaScript, Git}}{September 2025 -- Present}
\resumeItemListStart 
    \resumeItem{Designed a reusable e-commerce core logic library abstracting cart, checkout, product state, and authentication.} 
    \resumeItem{Integrated with multiple UI systems to enable rapid storefront development.}
    \resumeItem{Used to build 5+ production e-commerce websites, reducing duplicated logic.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://metro.octadine.com}{OctaDine}} $|$ \emph{Vue, Leaflet, Git}}{December 2024 -- March 2025}
\resumeItemListStart
    \resumeItem{Developed core features including reservations, ratings, and ordering workflows.}
    \resumeItem{Built a responsive digital menu with RTL support.}
    \resumeItem{Integrated Leaflet to define delivery zones and dynamic pricing.}  
    \resumeItem{Implemented a screen mode for in-store menu displays.}
    \resumeItem{Used across 25+ restaurants.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ReelTime} $|$ \emph{Laravel, PHP, MySQL, Blade, JavaScript}}{February 2026 -- April 2026}
\resumeItemListStart
    \resumeItem{Designed database schema, migrations, seeders, and Eloquent models, and built initial API endpoints.}
    \resumeItem{Implemented authentication with email verification via signed routes and role-based middleware for admin and profile access.}
    \resumeItem{Built the home page, watchlist frontend, and rating display logic across profile and admin views.}
    \resumeItem{Integrated the game API with leaderboard score tracking.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://chatandplay.onrender.com/}{chatNplay}} $|$ \emph{React.js, Socket.io, Node.js, Express, Firebase, WebRTC, three.js, Sass}}{June 2022 -- December 2022}
\resumeItemListStart
    \resumeItem{Built a real-time app supporting video, audio, and text communication.}
    \resumeItem{Implemented authentication using Firebase.}
    \resumeItem{Developed multiplayer games using real-time socket communication.}
    \resumeItem{Added live face filters using three.js.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://masters-finder.streamlit.app/}{Masters Finder}} $|$ \emph{Python, Selenium, scikit-learn, Streamlit}}{February 2025 -- April 2025}
\resumeItemListStart
    \resumeItem{Scraped and cleaned 1,000+ masters programs across 150+ universities from multiple sources using Selenium and BeautifulSoup.}
    \resumeItem{Built a TF-IDF + cosine similarity AI recommender and a funding classifier with feature importance reporting.}
    \resumeItem{Generated an interactive t-SNE course similarity map grouping programs by field and content proximity.}
    \resumeItem{Delivered a Streamlit dashboard with market visualizations and an acceptance probability calculator.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
    \textbf{Programming:} HTML, CSS, JavaScript/TypeScript, Dart, Python, C/C++/C\#, SQL, PHP \\
    \textbf{Frameworks:} Next.js, React, Vue.js, Node.js, Express.js, Flutter, Shopify (Liquid), Laravel \\
    \textbf{Libraries:} Leaflet.js, Three.js, Tailwind CSS, Sass/SCSS, Bootstrap, jQuery, Axios, React Router, Socket.io, WebRTC, scikit-learn, pandas, BeautifulSoup (bs4), Streamlit \\
    \textbf{Tools:} Git, Docker, Firebase, Supabase, Selenium \\
    \textbf{Infrastructure:} DNS \& Domain Management, Email Configuration, Deployment (Netlify, Cloudflare Pages, Render) \\
    \textbf{Languages:} English, Arabic
}}
\end{itemize}
\end{document}